---
title: "Assignment 1"
output: html_document
date: "2024-04-12"
---


```{r}
#install.packages('Amelia', dependencies = TRUE) 
library(Amelia)

#install.packages('corrplot', dependencies = TRUE)
library(corrplot)

#install.packages('caret', dependencies = TRUE) 
library(caret)

#install.packages('plotly', dependencies = TRUE)
library(plotly)

#install.packages('dplyr', dependencies = TRUE)
library(dplyr)

#install.packages('ggplot2', dependencies = TRUE)
library(ggplot2)

#install.packages('GGally', dependencies = TRUE)
library(GGally)
```

```{r}
library(stringr)
```


```{r}
setwd("C:/Mí Mí - please don't touch/Master AI/Semester 1 - 24/Predictive/A1")
getwd
```

```{r}
df <- read.csv(file="used_car.csv", header=TRUE, sep=",")
```

# Part B
# 1-C
# Nominal to Numeric

```{r}
unique(df$make_name)
numberic_brand <- df$make_name
Brand_BMW <- as.numeric(numberic_brand == "BMW")
Brand_AUDI <- as.numeric(numberic_brand == "Audi")
Brand_TOYOTA <- as.numeric(numberic_brand == "Toyota")
Brand_FORD <- as.numeric(numberic_brand == "Ford")
Brand_MES <- as.numeric(numberic_brand == "Mercedes-Benz")
Brand_VOL <- as.numeric(numberic_brand == "Volkswagen")
```

```{r}
unique(df$body_type)
numberic_bodytype <- df$body_type
Body_type_Sedan <- as.numeric(numberic_bodytype == "Sedan")
Body_type_SUV_Crossover <- as.numeric(numberic_bodytype == "SUV / Crossover")
Body_type_Hatchback <- as.numeric(numberic_bodytype == "Hatchback")
```

```{r}
unique(df$fuel_type)
numberic_fueltype <-df$fuel_type
Fuel_type_Gas <- as.numeric(numberic_fueltype == "Gasoline")
Fuel_type_Hybrid <- as.numeric(numberic_fueltype == "Hybrid")
Fuel_type_Diesel <- as.numeric(numberic_fueltype == "Diesel")
```

```{r}
unique(df$transmission)
numberic_transmission <- df$transmission
Transmission_Automatic <- as.numeric(numberic_transmission == "Automatic")
Transmission_Manual <- as.numeric(numberic_transmission == "Manual")
Transmission_Continuous <- as.numeric(numberic_transmission == "Continuously Variable Transmission")
Transmission_Dual <- as.numeric(numberic_transmission == "Dual Clutch")
```

```{r}
unique(df$wheel_system)
numberic_wheelsystem <- df$wheel_system
Wheel_system_All_Wheel <- as.numeric(numberic_wheelsystem == "All-Wheel Drive")
Wheel_system_Front_Wheel <- as.numeric(numberic_wheelsystem == "Front-Wheel Drive")
Wheel_system_Rear_Wheel <- as.numeric(numberic_wheelsystem == "Rear-Wheel Drive")
Wheel_system_Four_Wheel <- as.numeric(numberic_wheelsystem == "Four-Wheel Drive")
```


```{r}
unique(df$salvage)
numberic_salvage <- as.numeric(df$salvage)
```

#Ordinal to Numeric

```{r}
unique(df$condition)
condition_new <- factor(df$condition, levels = c("Excellent","Good","Fair"), labels = c(2,1,0))

unique(df$maximum_seating)
maximum_seating_new <- factor(df$maximum_seating, levels = c("8 seats","7 seats","6 seats","5 seats","4 seats"), labels = c(4,3,2,1,0))

unique(df$engine_cylinders)
engine_cylinders_new <- factor(df$engine_cylinders, levels = c("12 Cylinders","8 Cylinders","6 Cylinders","5 Cylinders","4 Cylinders","3 Cylinders"), labels = c(5,4,3,2,1,0)) 
```

```{r}
df$condition_new <- condition_new
df$maximum_seating_new <- maximum_seating_new
df$engine_cylinders_new <- engine_cylinders_new
df$numberic_salvage <- numberic_salvage
df$Wheel_system_All_Wheel <- Wheel_system_All_Wheel
df$Wheel_system_Front_Wheel <- Wheel_system_Front_Wheel
df$Wheel_system_Rear_Wheel <- Wheel_system_Rear_Wheel
df$Wheel_system_Four_Wheel <- Wheel_system_Four_Wheel
df$Transmission_Automatic <- Transmission_Automatic
df$Transmission_Manual <- Transmission_Manual
df$Transmission_Continuous <- Transmission_Continuous
df$Transmission_Dual <- Transmission_Dual
df$Fuel_type_Gas <- Fuel_type_Gas
df$Fuel_type_Hybrid <- Fuel_type_Hybrid
df$Fuel_type_Diesel <- Fuel_type_Diesel
df$Body_type_Sedan <- Body_type_Sedan
df$Body_type_SUV_Crossover <- Body_type_SUV_Crossover
df$Body_type_Hatchback <- Body_type_Hatchback
df$Brand_BMW <- Brand_BMW
df$Brand_AUDI <- Brand_AUDI
df$Brand_TOYOTA <- Brand_TOYOTA
df$Brand_FORD <- Brand_FORD
df$Brand_MES <- Brand_MES
df$Brand_VOL <- Brand_VOL
```

# 2
# 2-A

```{r}
summary(df)
```

```{r}
unique(df$front_legroom)
```


```{r}
unique_value_front <- "#FIELD!"
df <- df %>%
  filter(df$front_legroom != unique_value_front)
```

```{r}
df <- df[!df$front_legroom==" ",]
df <- df[!df$front_legroom=="",]
```

```{r}
unique(df$front_legroom)
```

```{r}
df$front_legroom = as.numeric(df$front_legroom)
```


```{r}
numeric_variables <- df %>% select(where(is.numeric), -c(numberic_salvage,Wheel_system_All_Wheel,Wheel_system_Front_Wheel ,Wheel_system_Rear_Wheel,Wheel_system_Four_Wheel,Transmission_Automatic ,Transmission_Manual ,Transmission_Continuous ,Transmission_Dual,Fuel_type_Gas ,Fuel_type_Hybrid,Fuel_type_Diesel,Body_type_Sedan,Body_type_SUV_Crossover,Body_type_Hatchback,Brand_BMW,Brand_AUDI,Brand_TOYOTA,Brand_FORD,Brand_MES,Brand_VOL))
numeric_variables
```

# 2-A-i
```{r}
summary(numeric_variables$price)
summary(numeric_variables$back_legroom)
summary(numeric_variables$city_fuel_economy)
summary(numeric_variables$engine_displacement)
summary(numeric_variables$front_legroom)
summary(numeric_variables$fuel_tank_volume)
summary(numeric_variables$height)
summary(numeric_variables$highway_fuel_economy)
summary(numeric_variables$horsepower)
summary(numeric_variables$length)
summary(numeric_variables$mileage)
summary(numeric_variables$wheelbase)
summary(numeric_variables$width)
```

```{r}
sd(numeric_variables$price)
sd(numeric_variables$back_legroom)
sd(numeric_variables$city_fuel_economy)
sd(numeric_variables$engine_displacement)
sd(numeric_variables$front_legroom)
sd(numeric_variables$fuel_tank_volume)
sd(numeric_variables$height)
sd(numeric_variables$highway_fuel_economy)
sd(numeric_variables$horsepower)
sd(numeric_variables$length)
sd(numeric_variables$mileage)
sd(numeric_variables$wheelbase)
sd(numeric_variables$width)
```


## 2-A-ii
```{r}
table(df$condition)
```

```{r}
table(df$maximum_seating)
```

```{r}
table(df$engine_cylinders)
```

```{r}
table(df$make_name)
```

```{r}
table(df$body_type)
```

```{r}
table(df$fuel_type)
```

```{r}
table(df$transmission)
```

```{r}
table(df$wheel_system)
```

```{r}
table(df$salvage)
```

```{r}
table(df$year)
```



#2-B

# Method to identify which diagram is suitable to find extreme values 
```{r}
data_range <- max(numeric_variables, na.rm = TRUE) - min(numeric_variables, na.rm = TRUE)

if (data_range > 50) {
  print("Boxplot")
} else if (data_range < 10) {
  print("Histogram of Data")
} else {
  print("Violin Plot of Data")
}
```


```{r}
boxplot(numeric_variables$front_legroom, main = "Front_legroom")
boxplot(numeric_variables$price, main = "Price")
boxplot(numeric_variables$back_legroom, main = "Back_legroom")
boxplot(numeric_variables$engine_displacement, main = "Engine_displacement")
boxplot(numeric_variables$city_fuel_economy, main = "City_fuel_economy")
boxplot(numeric_variables$fuel_tank_volume, main = "Fuel_tank_volume")
boxplot(numeric_variables$highway_fuel_economy, main = "Highway_fuel_economy")
boxplot(numeric_variables$height, main = "Height")
boxplot(numeric_variables$horsepower, main = "Horsepower")
boxplot(numeric_variables$length, main = "Length")
boxplot(numeric_variables$mileage, main = "Mileage")
boxplot(numeric_variables$wheelbase, main = "Wheelbase")
boxplot(numeric_variables$width, main = "Width")
```

# 3

```{r}
par(mfrow=c(1, 2))
hist(numeric_variables$mileage, breaks = 100, col="yellow", main ="Mileage")
hist(numeric_variables$price, breaks = 100, col="yellow", main ="Price")
hist(numeric_variables$back_legroom, breaks = 100, col="yellow", main ="back_legroom")
hist(numeric_variables$front_legroom, breaks = 100, col="yellow", main ="front_legroom")
hist(numeric_variables$city_fuel_economy, breaks = 100, col="yellow", main ="city_fuel_economy")
hist(numeric_variables$length, breaks = 100, col="yellow", main ="length")
hist(numeric_variables$height, breaks = 100, col="yellow", main ="height")
hist(numeric_variables$width, breaks = 100, col="yellow", main ="width")
hist(numeric_variables$engine_displacement, breaks = 100, col="yellow", main ="engine_displacement")
hist(numeric_variables$highway_fuel_economy, breaks = 100, col="yellow", main ="highway_fuel_economy")
hist(numeric_variables$horsepower, breaks = 100, col="yellow", main ="horsepower")
hist(numeric_variables$wheelbase, breaks = 100, col="yellow", main ="wheelbase")
hist(numeric_variables$fuel_tank_volume, breaks = 100, col="yellow", main ="fuel_tank_volume")
```


```{r}
plot(density(numeric_variables$engine_displacement, na.rm = TRUE))
plot(density(numeric_variables$back_legroom, na.rm = TRUE))
plot(density(numeric_variables$front_legroom, na.rm = TRUE))
plot(density(numeric_variables$mileage, na.rm = TRUE))
plot(density(numeric_variables$height, na.rm = TRUE))
plot(density(numeric_variables$length, na.rm = TRUE))
plot(density(numeric_variables$wheelbase, na.rm = TRUE))
plot(density(numeric_variables$horsepower, na.rm = TRUE))
plot(density(numeric_variables$highway_fuel_economy, na.rm = TRUE))
plot(density(numeric_variables$fuel_tank_volume, na.rm = TRUE))
plot(density(numeric_variables$city_fuel_economy, na.rm = TRUE))
plot(density(numeric_variables$width, na.rm = TRUE))
plot(density(numeric_variables$price, na.rm = TRUE))
```



```{r}
#install.packages("moments")
library(moments)
skewness(numeric_variables$engine_displacement, na.rm = TRUE)
```

```{r}
skewness(numeric_variables$back_legroom, na.rm = TRUE)
```

```{r}
skewness(numeric_variables$city_fuel_economy, na.rm = TRUE)
```

```{r}
skewness(numeric_variables$front_legroom, na.rm = TRUE)
```

```{r}
skewness(numeric_variables$fuel_tank_volume, na.rm = TRUE)
```

```{r}
skewness(numeric_variables$highway_fuel_economy, na.rm = TRUE)
```

```{r}
skewness(numeric_variables$height, na.rm = TRUE)
```

```{r}
skewness(numeric_variables$horsepower, na.rm = TRUE)
```

```{r}
skewness(numeric_variables$length, na.rm = TRUE)
```

```{r}
skewness(numeric_variables$mileage, na.rm = TRUE)
```

```{r}
skewness(numeric_variables$wheelbase, na.rm = TRUE)
```

```{r}
skewness(numeric_variables$width, na.rm = TRUE)
```

```{r}
skewness(numeric_variables$price, na.rm = TRUE)
```


#4
#4-A

```{r}
sapply(df, function(x) sum(is.na(x)))
```

#4-C

#Replacing N/A by 0
```{r}
# install.packages("psych")
library(psych)
```

```{r}
zeros <- df
is.na(zeros)
zeros[is.na(zeros)] <- 0
zeros[is.na(zeros)]
summary(zeros)
```


```{r}
mean(zeros$city_fuel_economy, na.rm = TRUE)
mean(df$city_fuel_economy, na.rm = TRUE)
```
```{r}
mean(zeros$mileage, na.rm = TRUE)
mean(df$mileage, na.rm = TRUE)
```

#Deleting records

```{r}
deleted <- df[complete.cases(numeric_variables),]
summary(deleted)
```

```{r}
mean(deleted$city_fuel_economy, na.rm = TRUE)
mean(df$city_fuel_economy, na.rm = TRUE)
```
```{r}
mean(deleted$mileage, na.rm = TRUE)
mean(df$mileage, na.rm = TRUE)
```

#Replacing with mean of the column 

```{r}
all_cleaned <- df
summary(all_cleaned$city_fuel_economy)
```
```{r}
mean(all_cleaned$city_fuel_economy, na.rm = TRUE)
```

```{r}
is.na(all_cleaned$city_fuel_economy)
all_cleaned$city_fuel_economy[is.na(all_cleaned$city_fuel_economy)]
```


```{r}
summary(all_cleaned$mileage)
```
```{r}
mean(all_cleaned$mileage, na.rm = TRUE)
```

```{r}
is.na(all_cleaned$mileage)
all_cleaned$mileage[is.na(all_cleaned$mileage)]
```


```{r}
all_cleaned$city_fuel_economy[is.na(all_cleaned$city_fuel_economy)] <- 0
all_cleaned$city_fuel_economy[is.na(all_cleaned$city_fuel_economy)] <- mean(all_cleaned$city_fuel_economy, na.rm = TRUE)
summary(all_cleaned$city_fuel_economy)
```

```{r}
all_cleaned$mileage[is.na(all_cleaned$mileage)] <- 0
all_cleaned$mileage[is.na(all_cleaned$mileage)] <- mean(all_cleaned$mileage, na.rm = TRUE)
summary(all_cleaned$mileage)
```


#Identify which method is the most suitable to use for this dataset
```{r}
plot(density(all_cleaned$city_fuel_economy), col="red",
     main="city_fuel_economy Original (Green) vs Transformed (Yellow)")
lines(density(zeros$city_fuel_economy, na.rm = TRUE), col="blue")
lines(density(deleted$city_fuel_economy, na.rm = TRUE), col="black")
lines(density(all_cleaned$city_fuel_economy, na.rm = TRUE), col="green")
```

```{r}
plot(density(all_cleaned$mileage), col="red",
     main="mileage Original (Green) vs Transformed (Yellow)")
lines(density(zeros$mileage, na.rm = TRUE), col="blue")
lines(density(deleted$mileage, na.rm = TRUE), col="black")
lines(density(all_cleaned$mileage, na.rm = TRUE), col="green")
```


#5

#5-A

#Data transform for right skewed variabels

```{r}
par(mfrow=c(1, 2))
trans_mileage <- log(all_cleaned$mileage)
hist(numeric_variables$mileage, breaks = 100, col="yellow", main ="original")
hist(transform_mileage, breaks = 100, col="yellow", main ="transformed")

trans_city_fuel_economy <- log(all_cleaned$city_fuel_economy)
hist(numeric_variables$city_fuel_economy, breaks = 100, col="yellow", main ="original")
hist(trans_city_fuel_economy, breaks = 100, col="yellow", main ="transformed")

trans_highway_fuel_economy <- log(all_cleaned$highway_fuel_economy)
hist(numeric_variables$highway_fuel_economy, breaks = 100, col="yellow", main ="original")
hist(trans_highway_fuel_economy, breaks = 100, col="yellow", main ="transformed")

trans_horsepower <- log(all_cleaned$horsepower)
hist(numeric_variables$horsepower, breaks = 100, col="yellow", main ="original")
hist(trans_horsepower, breaks = 100, col="yellow", main ="transformed")

trans_price <- log(all_cleaned$price)
hist(numeric_variables$price, breaks = 100, col="yellow", main ="original")
hist(trans_price, breaks = 100, col="yellow", main ="transformed")
```
#Choosing a target variable and remove useless variables

```{r}
target <- all_cleaned$price
new_df <- subset(all_cleaned, select = -c(price, city_fuel_economy, horsepower, condition, engine_cylinders, make_name, salvage, wheel_system ))
View(new_df)
```

```{r}
ggcorr(new_df, label=TRUE)
```

#5-B

#click 2 times, please

```{r}
cols <- c('mileage', 'highway_fuel_economy')
new_df[cols] <- log(new_df[cols])
```

```{r}
new_df[cols]$mileage[is.na(new_df[cols]$mileage)] <- 0
new_df[cols]$mileage[is.na(new_df[cols]$mileage)] <- mean(new_df[cols]$mileage, na.rm = TRUE)
summary(new_df[cols]$mileage)
```

```{r}
new_df$transform_mileage <- new_df[cols]$mileage
new_df$transform_highway_fuel_economy <- new_df[cols]$highway_fuel_economy
```


```{r}
L <- data.matrix(new_df)
corrL <- cor(L)
highlyCorrL <- findCorrelation(corrL, cutoff=0.7)
names(new_df)[highlyCorrL]
```

```{r}
remove_high_co <- subset(new_df, select = -c(highway_fuel_economy,height, body_type,wheelbase,Fuel_type_Gas,transform_highway_fuel_economy,Wheel_system_Front_Wheel,Body_type_SUV_Crossover,maximum_seating,Fuel_type_Hybrid,fuel_tank_volume,engine_displacement,Transmission_Automatic,transmission,transform_mileage))

ggcorr(remove_high_co, label=TRUE)
```
#Part C

# 1. Building Linear Model 
```{r}
remove_high_co$price <- all_cleaned$price
remove_high_co <- subset(remove_high_co,select = -c(daysonmarket, owner_count, fuel_type))
ggcorr(remove_high_co, label=TRUE)
```

```{r}
remove_high_co$price <- target
smp_size <- floor(2/3 * nrow(remove_high_co))
View(remove_high_co)
```

```{r}
set.seed(1)
remove_high_co <- remove_high_co[sample(nrow(remove_high_co)), ]
used_car.train <- remove_high_co[1:smp_size, ]
used_car.test <- remove_high_co[(smp_size+1):nrow(remove_high_co), ]
formula = price ~.
model <- lm(formula = formula, data = used_car.train)
summary(model)$coefficients
```

```{r}
as.formula(
  paste0("y ~ ", round(coefficients(model)[1],2), " + ", 
         paste(sprintf("%.2f * %s",coefficients(model)[-1], 
                       names(coefficients(model)[-1])), 
               collapse=" + ")
  )
)
```
```{r}
used_car.train$predicted.price <- predict(model, used_car.train)
```

```{r}
used_car.test$predicted.price <- predict(model, used_car.test)
```

```{r}
print("Actual Values")
head(used_car.test$price[1:5])
print("Predicted Values")
head(used_car.test$predicted.price[1:5])
```

```{r}
pl1 <- used_car.test %>% 
  ggplot(aes(price,predicted.price)) + 
  geom_point(alpha=0.5) + 
  stat_smooth(aes(colour='red')) + 
  xlab('Actual value of price') + 
  ylab('Predicted value of price')+ 
  theme_bw()
ggplotly(pl1)
```

```{r}
r_squared <- summary(model)$r.squared
print(paste("R Squared: ", r_squared))

error <- used_car.test$price-used_car.test$predicted.price
rmse <- sqrt(mean(error^2))
print(paste("Root Mean Square Error: ", rmse))
```

#Removing Transmission_Continuous

```{r}
lm_11 <- subset(remove_high_co,select = -c(Transmission_Continuous))
lm_11$price <- target
smp_size_11 <- floor(2/3 * nrow(lm_11))


set.seed(1)
lm_11 <- lm_11[sample(nrow(lm_11)), ]
used_car_11.train <- lm_11[1:smp_size_11, ]
used_car_11.test <- lm_11[(smp_size_11+1):nrow(lm_11), ]
formula = price ~.
model11 <- lm(formula = formula, data = used_car_11.train)
summary(model11)$coefficients
```


```{r}
as.formula(
  paste0("y ~ ", round(coefficients(model11)[1],2), " + ", 
         paste(sprintf("%.2f * %s",coefficients(model11)[-1], 
                       names(coefficients(model11)[-1])), 
               collapse=" + ")
  )
)
```


```{r}
used_car_11.train$predicted.price <- predict(model11, used_car_11.train)

used_car_11.test$predicted.price <- predict(model11, used_car_11.test)

```


```{r}
print("Actual Values")
head(used_car_11.test$price[1:5])
print("Predicted Values")
head(used_car_11.test$predicted.price[1:5])
```


```{r}
pl11 <- used_car_11.test %>% 
  ggplot(aes(price,predicted.price)) + 
  geom_point(alpha=0.5) + 
  stat_smooth(aes(colour='red')) + 
  xlab('Actual value of price') + 
  ylab('Predicted value of price')+ 
  theme_bw()
ggplotly(pl11)
```

```{r}
r_squared <- summary(model11)$r.squared
print(paste("R Squared: ", r_squared))

error <- used_car_11.test$price-used_car_11.test$predicted.price
rmse <- sqrt(mean(error^2))
print(paste("Root Mean Square Error: ", rmse))
```


#Removing width

```{r}
lm_12 <- subset(remove_high_co,select = - c(width))
lm_12$price <- target
smp_size_12 <- floor(2/3 * nrow(lm_12))
```

```{r}
set.seed(1)
lm_12 <- lm_12[sample(nrow(lm_12)), ]
used_car_12.train <- lm_12[1:smp_size_12, ]
used_car_12.test <- lm_12[(smp_size_12+1):nrow(lm_12), ]
formula = price ~.
model12 <- lm(formula = formula, data = used_car_12.train)
summary(model12)$coefficients
```

```{r}
as.formula(
  paste0("y ~ ", round(coefficients(model12)[1],2), " + ", 
         paste(sprintf("%.2f * %s",coefficients(model12)[-1], 
                       names(coefficients(model12)[-1])), 
               collapse=" + ")
  )
)
```

```{r}
used_car_12.train$predicted.price <- predict(model12, used_car_12.train)

used_car_12.test$predicted.price <- predict(model12, used_car_12.test)
```

```{r}
print("Actual Values")
head(used_car_12.test$price[1:5])
print("Predicted Values")
head(used_car_12.test$predicted.price[1:5])
```

```{r}
pl12 <- used_car_12.test %>% 
  ggplot(aes(price,predicted.price)) + 
  geom_point(alpha=0.5) + 
  stat_smooth(aes(colour='red')) + 
  xlab('Actual value of price') + 
  ylab('Predicted value of price')+ 
  theme_bw()
ggplotly(pl12)
```

```{r}
r_squared <- summary(model12)$r.squared
print(paste("R Squared: ", r_squared))

error <- used_car_12.test$price-used_car_12.test$predicted.price
rmse <- sqrt(mean(error^2))
print(paste("Root Mean Square Error: ", rmse))
```

# 2. Build decision tree

```{r}
library(Amelia)
missmap(remove_high_co,col=c('yellow','blue'),y.at=1,y.labels='',legend=TRUE)
```


```{r}
install.packages('rpart', dependencies = TRUE)
library(rpart)
install.packages('rpart.plot', dependencies = TRUE)
library(rpart.plot)
```

```{r}
smp_size_d <- floor(2/3 * nrow(remove_high_co)) 
nrow(remove_high_co)
```

```{r}
set.seed(2)
remove_high_co.selected <- remove_high_co[sample(nrow(remove_high_co)), ]
sample(5)
View(remove_high_co.selected)
```
```{r}
dt.train <- remove_high_co.selected[1:smp_size_d, ]  

dt.test <- remove_high_co.selected[(smp_size_d+1):nrow(remove_high_co.selected), ] 
```

```{r}
formula = price ~.
dtree <- rpart(formula, data=dt.train, method="anova")
dtree$variable.importance
```

```{r}
rpart.plot(dtree, type = 4, fallen.leaves = FALSE)
```

```{r}
print(dtree)
```
```{r}
predicted.price <- predict(dtree, dt.test)
```

```{r}
error <- dt.test$price - predicted.price
rmse <- sqrt(mean(error^2))
print(paste("Root Mean Square Error: ", rmse))
printcp(dtree)
```

# Prune 1

```{r}
dtree$cptable[which.min(dtree$cptable[,"xerror"]),"CP"]
```

```{r}
pruned_dtree <- prune(dtree, cp = 0.01) 
rpart.plot(pruned_dtree, type = 4, fallen.leaves = FALSE)
```

```{r}
predicted.pruned_dtree.price <- predict(pruned_dtree, dt.test)
```

```{r}
error_1 <- dt.test$price - predicted.pruned_dtree.price
rmse_1 <- sqrt(mean(error_1^2))
print(paste("Root Mean Square Error: ", rmse_1))
```

# Prune 2

```{r}
pruned_dtree_2 <- prune(dtree, cp = 0.013696) 
rpart.plot(pruned_dtree_2, type = 4, fallen.leaves = FALSE)
```

```{r}
predicted.pruned_dtree_2.price <- predict(pruned_dtree_2, dt.test)
```

```{r}
error_2 <- dt.test$price - predicted.pruned_dtree_2.price
rmse_2 <- sqrt(mean(error_2^2))
print(paste("Root Mean Square Error: ", rmse_2))
```

# Prune 3

```{r}
pruned_dtree_3 <- prune(dtree, cp = 0.016424) 
rpart.plot(pruned_dtree_3, type = 4, fallen.leaves = FALSE)
```

```{r}
predicted.pruned_dtree_3.price <- predict(pruned_dtree_3, dt.test)
```

```{r}
error_3 <- dt.test$price - predicted.pruned_dtree_3.price
rmse_3 <- sqrt(mean(error_3^2))
print(paste("Root Mean Square Error: ", rmse_3))
```










